Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-30 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:30	12:26:53	(Sun30.Aug)

% \ifCLASSOPTIONcompsoc
%    \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \else
%    \usepackage[caption=false,font=footnotesize]{subfig}
% \fi

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

If extra flexibility is desired, we can also estimate the variance by a weighted combination of local pixels
%
\begin{align}
E\big\{|z_p[x,n]|^2\big\} = \frac{1}{N_x N_k} \sumb{x'=x-X}{x+X} \sumb{n=n-K}{n+K} w_\text{prf}[x',n']\big| z_p[x',n'] \big|^2
\end{align}
%
where $N_x = 2X+1$ is the number of azimuth lines to average over, and $w_\text{prf}[x',n']$ is a normalized 2 dimensional weight function.

@@

Kaiser
Unlike the method described by Synne\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.

>>>>

\ifCLASSOPTIONcompsoc
   \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
   \usepackage[caption=false,font=footnotesize]{subfig}
\fi

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{\emph{Determining LCA window type}. Typical frequency responses for windows computed by a robust MVDR.\newline
\mbox{}\hfill\parbox[t]{.95\linewidth}{\emph{Goal: Determining LCA window type.}}
\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

If extra flexibility is desired, we can also estimate the variance by a weighted combination of local pixels
%
\begin{align}
E\big\{|z_p[x,n]|^2\big\} = \frac{1}{N_x N_k} \sumb{x'=x-X}{x+X} \sumb{n=n-K}{n+K} w_\text{prf}[x',n']\big| z_p[x',n'] \big|^2
\end{align}
%
where $N_x = 2X+1$ is the number of azimuth lines to average over, and $w_\text{prf}[x',n']$ is a normalized 2 dimensional weight function. \todo{Might want to be careful with this when we steer the windows, or drop it altogether}

@@

Kaiser

Unlike the method described by Synne\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.
